TODO: A Survey of StarCraft AI Techniques

### 2013-02-23 survey.tex
boing

These maps came in two flavors, namely 3 3-player maps:
\emph{Athena-II}, \emph{Neo Moon Glaive}, \emph{Tears of the Moon},
and 3 6-player maps:
\emph{Legacy}, \emph{River of Light}, and 
\emph{The Huntress 1.1}. 
We shall note that some bots consistently crashed on one
of the originally considered maps which has thus been replaced.
This is surprising as all maps are well known league play maps
or have been provided with the StarCraft Broodwar distribution
itself.

\ref{tab:cig2012}

\ref{fig:cig2012-results}
\ref{fig:cig2012-mapresults}

map ‘size‘ has an effect!
 Nova against BBQ: good on 6-player, bad on 3-player
 SCAIL and Adjutant better on 6-player, BBQ worse on 	6-player
 UAlbertaBot better on 6-player (due to scouting?)
 Nova consistently good against UAlbertaBot
 Xelnaga only bot to beat Skynet, but only on 3-player 	maps

Here are the 2 replays shown in the presentation: Xelnaga surprising Skynet with a targetted DTS attack on its probes, and Nova successfully luring UAlbertaBot's probes into its own base.

things (many) bots can‘t do:
 handle islands
 play zerg
 play maps of different sizes (!!!)
 play against random race
 finish off beaten opponent
 adapt to opponent strategy
 cooperate (no teamplay)

Setup and results for the CIG 2012 competition are 
here\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/starcraft-cig2012}}.

>>>>

These maps came in two flavors, namely 3 3-player maps:
\emph{Athena-II}, \emph{Neo Moon Glaive}, \emph{Tears of the Moon},
and 3 6-player maps:
\emph{Legacy}, \emph{River of Light}, and 
\emph{The Huntress 1.1}. 
We shall note that some bots consistently crashed on one
of the originally considered maps which has thus been replaced.
This is surprising as all maps are well known league play maps
or have been provided with the StarCraft Broodwar distribution
itself.
Setup, replays and results for the CIG 2012 competition can be found
here\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/starcraft-cig2012}}.

The overall results are displayed in table~\ref{tab:cig2012},
and the win rate evolution over time in figure~\ref{fig:cig2012-results}.
These are quite consistent with the results of the AIIDE 2012 competition,
so that we can conclude that the best bots are not very dependent on 
knowing the maps beforehand. However, the bot vs. bot win rates as
displayed in figure~\ref{fig:cig2012-mapresults} show some interesting
trends. On the maps with more possible start points, some bots do 
better than others, namely SCAIL, Adjutant, Nova, and UAlbertaBot,
the latter probably due to its very efficient scouting routine.
Some bots however suffer from the increased uncertainty about
the enemies position, namely Xelnaga and the BroodwarBotQ.

As already observed before in the previously described competitions,
there are also bots who consistently beat top ranked bots but have
severe problems against lower ranked bots. E.g., Xelnaga is especially
strong against Skynet on the 3-player maps (about 70\% wins). Reviewing
the replays led to the assumption that Xelnaga usually tries to attack
Skynet's probes with a dark templar strategy, and often succeeds. 
Nova does very well against the UAlbertaBot, and the replays show
that it sometimes succeeds to lure the probes into its own base, where
they get killed, leading to severe resource problems. However, we cannot
tell how often this happens as this would require to review every single
replay between the 2 bots. Summarizing, most bots seem to have improved,
which becomes clear if the nearly unchanged BTHAI bot is taken as a baseline.
In 2011, it won more than half of its qualifying games, in 2012 it came
out last with around 20\% wins. However, designing a bot in order to 
beat a top bot (as for Xelnaga with Skynet) leads to a very restricted
strategy that often leads to failure if playing against different bots.
Note that in the direct encounter between Xelnaga and AIUR, its ancestor,
Xelnaga looses consistently.

Nevertheless, from the observations we made during the tournament,
we can draw the conclusion that the available bots are still 
very constrained. No bot in the competition played the Zerg race,
which is surprising as the AIIDE 2010 winner (Overmind) did so.
Presumably, implementing a good Zerg strategy is more demanding
than for the Protoss or Terran races. Many bots consistently crashed
when playing against a random race built-in bot for testing, and
also did so when the map size was changed from $128\times 128$ to 
any other. Furthermore, every single bot sometimes failed to finish
off an already beaten opponent, such that the game had to be stopped
after a previously determined maximum time. It also seems that most of
the current bots are not very good at adapting their strategy to the
one of their opponent during a game, or at least (via the read/write
procedure of game information) within a series of games.
